External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for Paper ID 1047}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

We appreciate all the reviewers for their constructive comments, especially R2 for your encouraging comments.
\\
\textbf{R1's Questions}
\\
\textbf{Q1}: Overstatement of claims
\\
The noise in real world images are very complex and cannot be modeled by Poisson or other more complex distribution. Since it is too hard to explicitly model the real noise, we gave up designing good models for real noise. Instead, we turn to model the signals by statistical models such as mixture of Gaussian (MoG). We believe that as long as we model the signals accurately enough, we do not need strong priors for the noise, and hence we employ the $\ell_{2}$ norm for the residual errors. We admit that if we describe the noise with a more suitable model, the performance of our algorithm will be better. But this is not the major point of this paper, as pointed out by the title of this paper.
\\
\textbf{Q2}: There is nothing new in terms of the prior model ...
\\
When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL. However, this is not the exact work we have done in this paper. What we did is to employ the external priors learned from external data to guide the learning of internal priors which are more adaptive to the image being denoised. And we want to argue that this combination makes our model have stronger ability to characterize the signals in real noisy images. The results of two Poisson algorithm are listed in Table 1.
\\
\textbf{R2's Questions}
\\
\textbf{Q1}: The number and effect of parameters
\\
The key parameters of our model are the regularization parameter $\lambda$ and the number of atoms in external sub-dictionary,$r$. $r$ is very robust as long as it is in a reasonable range as demonstrated in experiments. $\lambda=0.001$ works well in the experiments. Other parameters are preset by hand and can work well as long as they are set in a reasonable range.
\\
\textbf{R3's Questions}
\\
\textbf{Q1}: hard to believe that it will work for all the cases
\\
We had tested our method on the two datasets which contains a lot of real noisy images for many cases, we will test our method and publish our code in the future for testing on more cases.
\\
\textbf{Q2}: not clear how to choose nonlocal similar patches
\\
Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing out.
\\
\textbf{Q3}: other noise types
\\
In this paper, we only deal with real noise in real noisy images.
\\
\textbf{Q4}: the likelihood term is Gaussian denoising
\\
Please kindly refer to the answers to \textbf{Q1} of \textbf{R1} and \textbf{Q3} above for this problem since the space is limited. 
\\
\textbf{Q5}: The competing algorithms would also work quite well
\\
We retained the TNRD, CSF or MLP model with the parameters set as the best performance cases as described in their corresponding paper, with Gaussian noise levels $\sigma = 5, 10, 15, 25, 35, 50, and 75$. We found that the best average PSNR results on the 15 and 60 images used in our paper happens with TNRD at $\sigma = 10$, which are 36.61dB and 38.32dB, respectively, 1.0dB and 0.57dB higher than the results with default parameter settings. But these results are still 0.55dB and 0.43dB, respectively, lower than the results of our method. The image qualities of TNRD at $\sigma = 10$ are still clearly inferior to those of our method. The whole retrained results are listed in Table 1.
\\
\textbf{Q6}: a single parameter setting for all the cases 
\\
The experiments demonstrate that a single parameter can deal with all the cases in the tested datasets. With more flexible parameters setting, the performance would be better and this is the line of our future work.
\\
\textbf{Q7}: why is the image resolution significantly smaller
\\
This is for smaller pdf size of the paper, and down scale the images would not affect much the image quality.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for Paper ID 1047}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

We appreciate all the reviewers for their constructive comments, especially R2 for your encouraging comments.
\\
\textbf{R1's Questions}
\\
\textbf{Q1}: Overstatement of claims
\\
The noise in real world images are very complex and cannot be modeled by Poisson or other more complex distribution. Since it is too hard to explicitly model the real noise, we gave up designing good models for real noise. Instead, we turn to model the signals by statistical models such as mixture of Gaussian (MoG). We believe that as long as we model the signals accurately enough, we do not need strong priors for the noise, and hence we employ the $\ell_{2}$ norm for the residual errors. We admit that if we describe the noise with a more suitable model, the performance of our algorithm will be better. But this is not the major point of this paper, as pointed out by the title of this paper.
\\
\textbf{Q2}: There is nothing new in terms of the prior model ...
\\
When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL. However, this is not the exact work we have done in this paper. What we did is to employ the external priors learned from external data to guide the learning of internal priors which are more adaptive to the image being denoised. And we want to argue that this combination makes our model have stronger ability to characterize the signals in real noisy images. The results of two Poisson algorithm are listed in Table 1. 
\begin{table}\vspace{1.5mm}
\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\vspace{-3mm}
\label{tab3}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
\\
\hline
PSNR &   34.58 & 34.52 & 36.19 & 37.40
\\
\hline
Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
\\
\hline
PSNR & 37.75  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
\\
\hline
\end{tabular}
\end{center}\vspace{-2.5mm}
\end{table}
\\
\textbf{R2's Questions}
\\
\textbf{Q1}: The number and effect of parameters
\\
The key parameters of our model are the regularization parameter $\lambda$ and the number of atoms in external sub-dictionary,$r$. $r$ is very robust as long as it is in a reasonable range as demonstrated in experiments. $\lambda=0.001$ works well in the experiments. Other parameters are preset by hand and can work well as long as they are set in a reasonable range.
\\
\textbf{R3's Questions}
\\
\textbf{Q1}: hard to believe that it will work for all the cases
\\
We had tested our method on the two datasets which contains a lot of real noisy images for many cases, we will test our method and publish our code in the future for testing on more cases.
\\
\textbf{Q2}: not clear how to choose nonlocal similar patches
\\
Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing out.
\\
\textbf{Q3}: other noise types
\\
In this paper, we only deal with real noise in real noisy images.
\\
\textbf{Q4}: the likelihood term is Gaussian denoising
\\
Please kindly refer to the answers to \textbf{Q1} of \textbf{R1} and \textbf{Q3} above for this problem since the space is limited. 
\\
\textbf{Q5}: The competing algorithms would also work quite well
\\
We retained the TNRD, CSF or MLP model with the parameters set as the best performance cases as described in their corresponding paper, with Gaussian noise levels $\sigma = 5, 10, 15, 25, 35, 50, and 75$. We found that the best average PSNR results on the 15 and 60 images used in our paper happens with TNRD at $\sigma = 10$, which are 36.61dB and 38.32dB, respectively, 1.0dB and 0.57dB higher than the results with default parameter settings. But these results are still 0.55dB and 0.43dB, respectively, lower than the results of our method. The image qualities of TNRD at $\sigma = 10$ are still clearly inferior to those of our method. The whole retrained results are listed in Table 1.
\\
\textbf{Q6}: a single parameter setting for all the cases 
\\
The experiments demonstrate that a single parameter can deal with all the cases in the tested datasets. With more flexible parameters setting, the performance would be better and this is the line of our future work.
\\
\textbf{Q7}: why is the image resolution significantly smaller
\\
This is for smaller pdf size of the paper, and down scale the images would not affect much the image quality.

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex

\\
\textbf{Q2}: There is nothing new in terms of the prior model ...
\\
When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL. However, this is not the exact work we have done in this paper. What we did is to employ the external priors learned from external data to guide the learning of internal priors which are more adaptive to the image being denoised. And we want to argue that this combination makes our model have stronger ability to characterize the signals in real noisy images. We evaluate two algorithms designed for Poisson noise reduction, NLSPCA \cite{nlpca} and \cite{makitalo2013optimal}. The results are listed in Table 1. Note that we had tune the parameters of these algorithms carefully to achieve their best performance.

@@

\\
\textbf{Q5}: The competing algorithms would also work quite well
\\
We retained the TNRD, CSF or MLP model with the carefully parameter tuning to achieve their corresponding best performance. For example, we retained these models with Gaussian noise levels in $\sigma = 5, 10, 15, 25, 35, 50$. We found that MLP achieves the best PSNR results on the 60 images used in our paper at $\sigma = 10$, which are 38.36dB. But this result is still 0.43dB lower than those of our method. The image qualities of MLP at $\sigma = 10$ are still clearly inferior to those of our method. The new results are listed in Table 1 in which we also evaluated the performance of two algorithms for Poisson noise removal, NLSPCA \cite{nlpca} and \cite{makitalo2013optimal}. 
 Methods& \textbf{NLSPCA} & \cite{makitalo2013optimal} & \textbf{MLP}&\textbf{CSF}
PSNR & 24.39  &  25.67 &  38.36 & 38.21
Methods & \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
PSNR & 38.32  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
\end{center}\vspace{-4mm}

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex

\\
\textbf{Q1}: Overstatement of claims
\\
\textbf{A1}: The noise in real world images are very complex and cannot be modeled by Poisson or other more complex distribution. Since it is too hard to explicitly model the real noise, we gave up designing good models for real noise. Instead, we turn to model the signals by statistical models such as mixture of Gaussian (MoG). We believe that as long as we model the signals accurately enough, we do not need strong priors for the noise, and hence we employ the $\ell_{2}$ norm for the residual errors. We admit that if we describe the noise with a more suitable model, the performance of our algorithm will be better. But this is not the major point of this paper, as pointed out by the title of this paper.

@@

\\
\textbf{Q2}: There is nothing new in terms of the prior model ...
\\
\textbf{A2}: When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL. However, this is not the exact work we have done in this paper. What we did is to employ the external priors learned from external data to guide the learning of internal priors which are more adaptive to the image being denoised. And we want to argue that this combination makes our model have stronger ability to characterize the signals in real noisy images. We evaluate two algorithms designed for Poisson noise reduction, NLSPCA \cite{nlpca} and \cite{makitalo2013optimal}. The results are listed in Table 1. Note that we had tune the parameters of these algorithms carefully to achieve their best performance.

@@

\\
\textbf{Q1}: The number and effect of parameters
\\
\textbf{A1}: The key parameters of our model are the regularization parameter $\lambda$ and the number of atoms in external sub-dictionary,$r$. $r$ is very robust as long as it is in a reasonable range as demonstrated in experiments. $\lambda=0.001$ works well in the experiments. Other parameters are preset by hand and can work well as long as they are set in a reasonable range.

@@

\\
\textbf{Q1}: hard to believe that it will work for all the cases
\\
\textbf{A1}: We had tested our method on the two datasets which contains a lot of real noisy images for many cases, we will test our method and publish our code in the future for testing on more cases.

@@

\\
\textbf{Q2}: not clear how to choose nonlocal similar patches
\\
\textbf{A2}: Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing it out.

@@

\\
\textbf{Q3}: other noise types
\\
\textbf{A3}: In this paper, we only deal with real noise in real noisy images. Other noise types will be considered in future work.

@@

\\
\textbf{Q4}: the likelihood term is Gaussian denoising
\\
\textbf{A4}: Please kindly refer to the answers \textbf{A1} to \textbf{Q1} of \textbf{R1} and \textbf{A3} to \textbf{Q3} above for this problem since the space is limited. 

@@

\\
\textbf{Q5}: The competing algorithms would also work quite well
\\
\textbf{A5}: We retained the TNRD, CSF or MLP model with the carefully parameter tuning to achieve their corresponding best performance. For example, we retained these models with Gaussian noise levels in $\sigma = 5, 10, 15, 25, 35, 50$. We found that MLP achieves the best PSNR results on the 60 images used in our paper at $\sigma = 10$, which are 38.36dB. But this result is still 0.43dB lower than those of our method. The image qualities of MLP at $\sigma = 10$ are still clearly inferior to those of our method. The new results are listed in Table 1 in which we also evaluated the performance of two algorithms for Poisson noise removal, NLSPCA \cite{nlpca} and \cite{makitalo2013optimal}. 

@@

\\
\textbf{Q6}: a single parameter setting for all the cases 
\\
\textbf{A6}: The experiments demonstrate that a single parameter can deal with all the cases in the tested datasets. With more flexible parameters setting, the performance would be better and this is the line of our future work.

@@

\\
\textbf{Q7}: why is the image resolution significantly smaller
\\
\textbf{A7}: This is for smaller pdf size of the paper, and down scale the images would not affect much the image quality.

### 2017-02-07 egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{1047} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Authors' Response to the Review of Paper 1047\\External Prior Guided Internal Prior Learning for Real Noisy Image Denoising}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We appreciate all the reviewers for their constructive comments. We regret that R1 and R3 had obvious misunderstanding on our work. We sincerely ask them to read our paper again. What below are our responses to all the reviewers' comments.

\vspace{-1mm}
\section{Non-Gaussian noise (R1\&R3)}
In this work we presented an effective algorithm for real noisy image denoising, but we didn't claim that we developed a new model for non-Gaussian noise. The noise in real world images is too complex to be modeled by Poisson or other simple distributions. Therefore, we focused on the modeling of image priors, while using the simple $l_{2}$-norm to measure the residual. We agree that if a more complex noise model is used, the performance of our algorithm can be better. However, this is not the focus of this paper. Using the simple $l_{2}$-norm on residual, our method has already achieved very competitive results, which clearly demonstrated the effectiveness of our image prior model.

Both R1 and R3 asked us to compare with Poisson noise removal methods. In Table 1 we compared with 2 state-of-the-art Poisson noise reduction methods \cite{Makitalo2013Optimal} and \cite{Salmon}. Note that we have tuned their parameters carefully to achieve their best performance. Neither \cite{Makitalo2013Optimal} nor \cite{Salmon} works well. This is because real world noise is much more complex than Poisson.

\begin{table}[h!]
\begin{center}
\caption{Average PSNR (dB) results of different methods on 60 real noisy images from \cite{Nam2016A}}
\begin{tabular}{|l|c|c|c|c|}
  \hline
  \textbf{Methods}                             &\cite{Makitalo2013Optimal}          &\cite{Salmon}       &MLP &CSF        \\
  \hline
  PSNR                    &  24.39                     &   25.67 &38.36 &38.21                           \\
  \hline
  \textbf{Methods}                             &TNRD          &NI       &NC &Ours        \\
  \hline
  PSNR                    &  38.32                     &   36.53 &37.57 &\textbf{38.75}                           \\
  \hline
\end{tabular}
\end{center}
\label{tab:1}
\end{table}

\vspace{-9mm}
\section{Novelty of our prior model (R1\&R3)}
Most of the previous denoising methods either learn external priors or learn internal priors. Our method is among the first methods to learn hybrid prior models. We first learn external GMM priors from clean images (this part is basically the same as Zoran and Weiss' 2011 work and we have made this very clear in our paper), and then use the GMM prior to guide the learning of image internal priors (this part is totally new). We want to argue that this is a novel contribution and our method shows state-of-the-art performance on real noisy image denoising.

\section{The effect of parameters (R2)}
There are 6 model parameters in our method and all of them are fixed in our experiments (please refer to the section of implementation details). Based on our experience, our method will not be affected much when these parameters vary around our default setting. The most sensitive parameter is the regularization parameter $\lambda$ in Eq. (5), and we set $\lambda$=0.001 by experience.

\section{The setting of competing algorithms (R3)}
We re-trained carefully the TNRD, CSF and MLP models with Gaussian noise levels $\sigma$ = 5, 10, 15, 25, 35, 50, and re-run the experiments. The new results are listed in Table 1. One can see that our method is still the best one. The $2^{nd}$ best method is MLP with $\sigma$ =10, which is 0.39dB lower than our method.

\section{Single parameter setting for all cases (R3)}
Yes we do use a single parameter setting and it works well on the two very different datasets. Actually this is not a magic because the key parameter $\lambda_{j}$ (Eq. (5) in the main paper) in our algorithm is adaptively determined based on the statistics of the external and internal data. This is one advantage of our algorithm.

\section{Nonlocal similar patches (R3)}
Yes we chose similar patches based on the Euclidean distance. We will make this clear in the revised paper. A stronger patch matching algorithm can make our algorithm perform better but will increase the complexity.

\section{Image resolution (R3)}
The reason we down-sampled the images is to make the size of PDF file smaller. Actually, if we view the images with original size, the better visual quality of our method over other denoising methods will be more obvious.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}
